% !TEX TS-program = lualatex
\documentclass[12pt,openany]{book}
%TC:ignore 
% This is all the packages and settings and so on.
% It is using custom fonts that needs to be installed on the computer. If they are not present, they have to be added manually.
\input{setup/settings.tex}

% Defining files for bibliography
\addbibresource{references.bib}
% Add a second bibliography file for the second author to allow
% both to update it through the mendeley integration.
% \addbibresource{ref-author-2.bib}

% Defining document information
\title{Optimal Gait Control of Soft Quadruped Robot by Model-based Reinforcement Learning}
% \newcommand{\subtitle}{TAN Kaige}
\author{NIU Xuezhi}
\let\tableofcontents\etoctableofcontents
\begin{document}

\setstretch{1.25}

% The front page of the document
\pagenumbering{Roman}
\include{setup/title-page}
\include{sections/0-pre-content}

\pagenumbering{arabic}
\section{checklist}
It should be no longer than 10.000 words, not counting references and appendices.
 
It should include the following sections (note that this supersedes the instructions in Appendix B in the master thesis handbook):
 \begin{enumerate}
     \item Abstract: An abstract that allows an "informed reader" to grasp the contents of the report. This abstract should be 100\% finished at the 80\%-draft of the report.
     \item Introduction: Define the background of your project, the purpose of the report, specific descriptions of problems, your research questions, any limitations to the scope of your investigation, and (briefly) your chosen methodology.
     \item Related Work / Theoretical Background / Theoretical Framework: It is necessary to describe the relevant, scientific background knowledge concerning the area in which you will perform your thesis work. One goal of this section is to analyse the literature reviewed and thus specify the direction of your project work. The main goal is for you to build on and expand your existing knowledge to assist you in dealing with the task at hand. This section is ideally structured as describing related work (scientific papers that perform variants of the same investigation as you do), as a theoretical background (scientific papers that deal with the same problem area as you do), or as a theoretical framework (scientific papers that you use to create a theoretical model for explaining your results).
     \item Methodology: Describe the scientific methodology that you have used in your investigation, using an appropriate scientific textbook as a reference. You have been introduced to case studies and experiments in the research methodology course, but you can use other methodologies if you can motivate it. For a case study this section includes a detailed description if your chosen case(s). An experimental study can provide hypotheses here, or in Section B (whichever is most easily read). This section also includes a description of the choices you have made to support the internal validity, external validity and reliability of your investigation.
     
     Note that methodologies can be described as being quantitative or qualitative, but these two words do not describe any specific methodology by themselves.
     \item Result/Analysis: Present the results from your study. If appropriate for readability, this section can succinctly compare your empirical results with existing theory in the field and/or your hypotheses. This interpretation/analysis should then be directly related to the papers described in Section B.
     \item Discussion: In this section you discuss your findings. This discussion should answer your research questions in relation to the papers described in Section B, and possibly other relevant papers. In other words, this section should put your results into perspective considering the results from other studies, the wider discussion in your problem area and/or considering the theoretical models you have used.

      Note that this can include an evaluation of your results to highlight e.g., performance improvements of a solution you have investigated, but that this is not enough on its own – all improvements must be put into perspective considering relevant aspects of the discussion in associated papers.

      This section can also include a “limitations” subsection, which describes limitations to your findings - such as when it is not appropriate to trust them. This section should also include a discussion of your results and investigation in relation to ethical, social or sustainability issues.
      \item Conclusions and Future Work: Describe the conclusions of your work and give recommendations on how to proceed with the work.
      \item Appendices: Important, but complementary material/results can be placed in appendices. This includes details of any implementation (practical work stages, etc.), large data sets, etc.”
 \end{enumerate}
\newgeometry{left=0cm,bottom=0cm,right=0cm,top=0cm}
\begin{figure}[hp]
\centering
    \begin{ganttchart}[vgrid, hgrid,
    bar label font=\footnotesize,
    group label font=\small\bfseries,
    today=13,
    today label=Today,
    today rule/.style={draw=black!64,
      dash pattern=on 3.5pt off 4.5pt,
      line width=1.5pt},
    milestone inline label node/.append style={left=2ex},
    inline]{5}{36}
        \gantttitle{Weeks of 2023}{32} \\
        \gantttitlelist{5,...,36}{1} \\
        
        \ganttgroup[progress=100]{Project setup}{5}{11} \\
        \ganttbar[inline = false, progress=100]{Literature review}{5}{8} \\
        \ganttbar[inline = false, progress=100]{Develop thesis proposal}{5}{9} \\
        \ganttbar[inline = false, progress=100]{Develop research plan}{8}{11} \\
        
        \ganttgroup[progress=50]{Model Development}{10}{14} \\
        \ganttbar[inline = false, progress=100]{Feature extraction}{10}{11} \\
        \ganttbar[inline = false, progress=70]{Collect data}{11}{13} \\
        \ganttbar[inline = false, progress=50]{Train surrogate model}{13}{14} \\
        
        
        \ganttgroup[progress=5]{Algorithm Development}{14}{19} \\
        \ganttbar[inline = false, progress=50]{Implement model}{14}{15} \\
        \ganttbar[inline = false, progress=10]{Design MBRL algorithm}{15}{17} \\
        \ganttbar[inline = false, progress=0]{Simulate algorithm}{17}{19} \\
        
        \ganttgroup[progress=0]{Experiment \& Validation}{20}{25} \\
        \ganttbar[inline = false, progress=0]{Test MFRL algorithm}{20}{20} \\
        \ganttbar[inline = false, progress=0]{Conduct experiments}{21}{23} \\
        \ganttbar[inline = false, progress=0]{Analyze results}{24}{25} \\
        
        \ganttgroup[progress=7, group progress label anchor=south]{Report Writing}{10}{35} \\
        \ganttbar[inline = false, progress=15]{Writing thesis draft}{10}{26} \\
        \ganttmilestone{80\% report}{26} \\
        \ganttbar[inline = false, progress=0, bar progress label anchor=west]{Supervisor review}{27}{34} \\
        \ganttmilestone{Presentation}{35} \\
        \ganttbar[inline = false, progress=0, bar progress label anchor=west]{Revise thesis}{34}{35} \\
        \ganttmilestone{End of thesis}{36} 
        \ganttlink{elem17}{elem18}
        \ganttlink{elem18}{elem19}
        \ganttlink{elem19}{elem20}
        \ganttlink{elem20}{elem21}
        \ganttlink{elem21}{elem22}
    \end{ganttchart}
    
    \caption{Gantt chart of this thesis project.}
    \label{fig:Gantt}
\end{figure}
\restoregeometry

%TC:endignore 
\include{sections/1-introduction}
\include{sections/2-background}
\include{sections/3-method}
\include{sections/4-work}
\include{sections/5-results}
\include{sections/6-conclusions}

% \include{content}
%TC:ignore 
\newpage
% \addcontentsline{toc}{chapter}{References}
% \pagestyle{empty}
\setstretch{1}
% \fontsize{5}{0}
\footerfont
\printbibliography[heading=bibintoc]

\include{sections/appendices}
\include{setup/back-cover}
%TC:endignore 
\end{document}
